Issues with Dynamical Measurements Across the Disk

### 2019-02-26 paper/ms.tex
Expand a little on effect on Jz

The situation is more forgiving for the study of thick-disk-like orbits, where
an $\mathcal{O}(1)$ systematic error in $J_z$ requires a larger midplane
deviation (\thickcolor horizontal line in Figure \ref{fig:range_deltaphi})
corresponding to $\Delta \phi >$ XX, YY, and ZZ radians or $\lambda \sim$ XX,
YY, and ZZ parsecs. For stars on halo-like orbits, extending the local
coordinate system globally is not likely to cause serious problems, since the
midplane deviations are relatively small compared to those needed to produce
$\mathcal{O}(1)$ systematic errors in the actions (\halocolor horizontal line
in Figure \ref{fig:range_deltaphi}). However, we caution that the tendency of
these midplane deviations is to \emph{inflate} the value of $J_z$ for thin
disk stars in an extremely non-Gaussian way (Figure \ref{fig:Jz_hist}),
scattering them into the region of action space normally associated with
different stellar populations and possibly contributing to confusion there.

>>>>

The situation is more forgiving for the study of thick-disk-like orbits, where
an $\mathcal{O}(1)$ systematic error in $J_z$ requires a larger midplane
deviation (\thickcolor horizontal line in Figure \ref{fig:range_deltaphi})
corresponding to $\Delta \phi >$ XX, YY, and ZZ radians or $\lambda \sim$ XX,
YY, and ZZ parsecs. For stars on halo-like orbits, extending the local
coordinate system globally is not likely to cause serious problems, since the
midplane deviations are relatively small compared to those needed to produce
$\mathcal{O}(1)$ systematic errors in the actions (\halocolor horizontal line
in Figure \ref{fig:range_deltaphi}). However, we caution that the tendency of
these midplane deviations is to \emph{inflate} the value of $J_z$ whenever the
midplane deviation is $\gtrsim z_{\text{max}}$, scattering them into the
region of action space normally associated with different stellar populations
and possibly contributing to confusion there. This inflation is extremely
non-Gaussian (as the induced error is for all orbits, e.g.
Figure~\ref{fig:Jz_hist}), and is particularly troubling for the case of thin
disk stars, where the necessary midplane deviation is
$\sim50\textup{--}100\,\pc$.
